\section{Automatic periodic data backups. E.g.: app tasker}\label{sec:ch8}
To create the task that automatically exports the specific data listed in \cref{subsec:mob_to_pc}, do the following:

This is like a double safety data backup and data overview for convenience.

\begin{enumerate}
    \item open tasker
    \item then in the top bar where it says "profiles.. tasks .." hold "tasks>import" then select the file named "CopyWhatsappV0.prj.xml" import that task.
    \item You can create that file by opening a notepad and pasting the content of \cref{app:A} in it and then renaming the .txt file to a .xml file.
    \item that copies all your whatsap data into a folder on the external storage (drive named 17EE-2356) named: WhatsAppExport
    \item Todo: verify this method works.
\end{enumerate}


\subsection{Export automatic periodic backups with Tasker}
Using tasker you can export the data manually from internal SD to External SD. To export your whatsapp media, import the tasker project=(task executed every xx [time span] listed in \cref{app:A}. \cref{app:A} contains the the xml code for the .xml file that is a tasker project (copy the text into a notepad and store it as WhatsappExport.xml). If you import this project it will automaticallly export your files every night to external SD. In \cref{app:F} a different tasker project is listed that exports all non-Whatsapp media to your external SD. %TODO: list exact files and folders, and folder types
%TODO: Make it dynamic, so that it asks the user to select the folder locations once.
\subsubsection{Download files from phone to laptop through USB}\label{subsec:mob_to_pc}
\begin{enumerate}
    \item Open 
\begin{verbatim}
../Minimal ADB and Fastboot_techbeasts/py_cmd.exe    
\end{verbatim}

    \item Connect Phone through USB with PC. (Verify it is connected G, by typing
\begin{verbatim}
"adb devices" in py_cmd.exe (should return a code for the device))    
\end{verbatim}
    \item Enter the following commands to copy their respective folder:
\begin{verbatim}
adb pull "/storage/17EE-2356/WhatsAppExport" "E:\2018-09-22 backups\Android\WhatsAppExport" 

adb pull "/storage/17EE-2356/DCIM" "E:\2018-09-22 backups\Android\DCIM"

adb pull "/storage/17EE-2356/call records" "E:\2018-09-22 backups\Android\call records" 

adb pull "/storage/17EE-2356/Contacts" "E:\2018-09-22 backups\Android\Contacts"

adb pull "/storage/17EE-2356/titanium backups" "E:\2018-09-22 backups\Android\titanium backups"    
\end{verbatim}
\end{enumerate}
\subsection{List of data that is exported: (this data is only put there if you have automated the tasker backup as described in \cref{sec:tasker_auto_backup}}
\begin{enumerate} 
    \item WhatsAppExport
    \item DCIM
    \item call records
    \item Contacts
    \item Titanium backups
\end{enumerate}
\subsubsection{Create a batchscript to do the absorbing.}
Specifications:
\begin{enumerate}
    \item get list of folders on phone.
    \item get single destination folder
    \item automatically create subdestinations in destination folder based on list of folders on phone, if the destinations do not already exist.
    \item for all files in folder pull. (duplicate files are just overwritten)
    \item \textbf{Todo:} for all files: if file is created a week ago, and file is on pc in destination folder, then delete on phone.
    \item \textbf{Todo:} Structure backup location and make it dynamic.
\end{enumerate}

